An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-27 VLDB2026/main.tex
Merge branch 'main' of https://github.com/zhujx001/Hybrid-ANNS

	(5)\textbf{ Recommendations and Challenges.}
	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries. These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution. Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.

>>>>

	(5)\textbf{ Recommendations and Challenges.}
	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries. These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, the high indexing costs of graph-based methods, and the sensitivity of algorithms to data distribution. \textcolor{yellow} {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}
